Estimating duration in the presence of misclassification

### 2024-07-31 cis-imperfect-testing.tex
"data" is plural
Rob first p109 comment (on assumptions)

The CIS data provides evidence for the test sensitivity declining over the course of an episode.
\Cref{imperf-test:fig:bounding-cis-sensitivity} demonstrates this by using the following classification for test results.
\begin{enumerate}
    \item All positive results are true positives.
    \item All intermittent negatives are false negatives.
    \item The negative at the end of an episode is a possible false negative.
    \item All other negatives are true negatives.
\end{enumerate}
The classification assumes that the probability of two false negative tests at the end of an episode is negligible.
As test sensitivity is the proportion of individuals who should test positive that do so, it can be empirically calculated as number of true positives / (number of true positives + number of false negatives).
This can be bounded by assuming either all or none of the possible false negatives (group 3) are in fact false negatives.
I calculate the test sensitivity for each day, where the day of the first positive result in an episode is day zero.
Day zero is an unknown number of days after the episode's latent true beginning time.
% In \cref{imperf-test:fig:bounding-cis-sensitivity} we consider the values produced by assuming the negative following the last positive in an episode could be either a true or false negative as a function of time since the individual was detected (\ie the first positive test in the episode).
I generate broad bounds, suggestive of a declining test sensitivity over the course of an episode (see \cref{imperf-test:fig:bounding-cis-sensitivity}).
Small numbers of tests mean that the series is noisy near the start and the end, such as both bounds being 0 on some days after day 40.
However, the general trend is clear.
\begin{figure}
  \includegraphics{cis-imperfect-testing/test-sens-bound}
  \caption[Bounding test sensitivity using CIS data]{
    Bounding the test sensitivity using CIS data as a function of time since the infection was detected.
  }
  \label{imperf-test:fig:bounding-cis-sensitivity}
\end{figure}

@@

In this section, I introduce a simple model of false negatives (\ie allowing $\psens < 1$) into the posterior density derived in \cref{E-perf-test:sec:model}.
Using a simple model, in particular a constant test sensitivity, means calculating the likelihood remains tractable.

@@

For tractability, assume that the negative test bounding the start of the episode, on day $l_k^{(b)}-1$, is a true negative.
This assumption is reasonable because, since a positive test follows at $r_k^{(b)}$, the negative at $l_k^{(b)}-1$ is likely early in the infection and the test sensitivity is high early in an infection.
True negatives occur with probability 1, and hence this test does not contribute to the likelihood.

@@

For there to be no subsequent positive tests, all tests up until day $e_j$ are false negatives.
I assume there is a negligible probability of two false negatives.
Therefore, this can only occur if the episode ends before another test.
Denote the number of days between $b_j$ and the test following the false negative as $\tau^2_{\sched_{i(j)}}(b_j) \stackrel{\text{def}}{=} \tau_{\sched_{i(j)}}(\tau_{\sched_{i(j)}}(b_j) + 1)$.
Then, the episode ends before this test if $d_j \leq \tau^2_{\sched_{i(j)}}(b_j)$.

>>>>

The CIS data provide evidence for the test sensitivity declining over the course of an episode.
\Cref{imperf-test:fig:bounding-cis-sensitivity} demonstrates this by using the following classification for test results.
\begin{enumerate}
    \item All positive results are true positives.
    \item All intermittent negatives are false negatives.
    \item The negative at the end of an episode is a possible false negative.
    \item All other negatives are true negatives.
\end{enumerate}
The classification assumes that the probability of two false negative tests at the end of an episode is negligible.
As test sensitivity is the proportion of individuals who should test positive that do so, it can be empirically calculated as number of true positives / (number of true positives + number of false negatives).
This can be bounded by assuming either all or none of the possible false negatives (group 3) are in fact false negatives.
I calculate the test sensitivity for each day, where the day of the first positive result in an episode is day zero.
Day zero is an unknown number of days after the episode's latent true beginning time.
% In \cref{imperf-test:fig:bounding-cis-sensitivity} we consider the values produced by assuming the negative following the last positive in an episode could be either a true or false negative as a function of time since the individual was detected (\ie the first positive test in the episode).
I generate broad bounds, suggestive of a declining test sensitivity over the course of an episode (see \cref{imperf-test:fig:bounding-cis-sensitivity}).
Small numbers of tests mean that the series is noisy near the start and the end, such as both bounds being 0 on some days after day 40.
However, the general trend is clear.
\begin{figure}
  \includegraphics{cis-imperfect-testing/test-sens-bound}
  \caption[Bounding test sensitivity using CIS data]{
    Bounding the test sensitivity using CIS data as a function of time since the infection was detected.
  }
  \label{imperf-test:fig:bounding-cis-sensitivity}
\end{figure}

@@

In this section, I introduce a simple model of false negatives (\ie allowing $\psens < 1$) into the posterior density derived in \cref{E-perf-test:sec:model}; I continue to assume the probability of a false positive is negligible.
Using a simple model, in particular a constant test sensitivity, means calculating the likelihood remains tractable.
Additionally, I limit the number of permutations of false negative and true positive tests that I consider have non-negligible probability.
Specifically, I assume that, if $i(j)$ is tested during infection episode $j$, either: the individual has a single false negative test and the episode ends before their next test, or the first test is a false positive test.
This assumption is reasonable because false negatives normally occur when the viral load is low, which is normally late in the infection episode.
For the same reason, I assume there is at most one false negative test following the final true positive test in the episode.

@@

By assumption, the negative test bounding the start of the episode, on day $l_k^{(b)}-1$, is a true negative.
True negatives occur with probability 1, and hence this test does not contribute to the likelihood.

@@

For there to be no subsequent positive tests, all tests up until day $e_j$ are false negatives.
By assumption, there is a negligible probability of two false negatives.
Therefore, this can only occur if the episode ends before another test.
Denote the number of days between $b_j$ and the test following the false negative as $\tau^2_{\sched_{i(j)}}(b_j) \stackrel{\text{def}}{=} \tau_{\sched_{i(j)}}(\tau_{\sched_{i(j)}}(b_j) + 1)$.
Then, the episode ends before this test if $d_j \leq \tau^2_{\sched_{i(j)}}(b_j)$.
